Twisted 11-dimensional supergravity, I

### 2021-08-06 draft.tex
more hash

\title{Twisted 11-dimensional supergravity, I}
\author{Surya Raghavendran}
\address{Perimeter Institute}
\email{??}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics, University of Edinburgh, Edinburgh, UK}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
to do
\end{abstract}
\maketitle

@@

Let $\cL$ be the 
We consider the following two automorphisms

The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.

We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
Recall we have two types of elements $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
\end{align*}
For $k \geq 2$ the general formula for the $k$-ary bracket is 
\[
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
\]

@@

Recall further that we constructed two equivalent descriptions of the BF theory based on divergence-free holomorphic vector fields above. Since we are now in the context of a nondegenerate BV theory, the differential is Hamiltonian, and can be incorporated into the action functional by including a quadratic term; we do this from now on. The first action functional is obtained by considering the BF theory associated to the natural dg Lie structure on the complex modeling divergence-free vector fields (inherited from the Schouten bracket). This takes the form
\deq{
  I_\strict = \beta\partial_\Omega \mu + \frac{1}{2} \gamma [\mu,\mu] + \beta[\mu,\nu].
}
The other action is of infinite order, and is related to the BCOV action functional via the procedure outlined above \ingmar{or somewhere}. Explicitly, this action functional is given by 
\deq{
  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2,
}

\subsection{A family of deformations}

@@

>>>>

\title{Twisted 11-dimensional supergravity, I}
\author{Surya Raghavendran}
\address{Perimeter Institute for Theoretical Physics \\ 31 Caroline Street North \\ 
Waterloo, Ontario N2L 2Y5\\ Canada}
\email{??}
\author{Ingmar Saberi}
\address{Ludwig-Maximilians-Universit\"at M\"unchen \\ Fakult\"at f\"ur Physik \\ Theresienstra\ss{}e 37 \\ 80333 M\"unchen \\ Deutschland}
\email{i.saberi@physik.uni-muenchen.de}
\author{Brian R. Williams}
\address{School of Mathematics \\ University of Edinburgh \\ Edinburgh EH9 3FD \\ Scotland}
\email{brian.williams@ed.ac.uk}
\begin{abstract}
to do
\end{abstract}
\maketitle

\newpage

@@

Let $\cL$ be the sheaf~\eqref{eqn:cplx1} of dg Lie algebras resolving divergence-free vector fields constructed above.
We consider the following automorphism of~$C^\bu(\cL)$, defined by its action on generators:\ingmar{notation for operators vs fields}
\deq[eq:newbase]{
%    \Psi_\infty:  \nu &\mapsto -\frac{\nu}{1-\nu}, \quad \mu \mapsto -\mu \\
    \Psi_\infty: \nu \mapsto 1 - e^{-\nu}, \quad \mu \mapsto e^\nu \mu.
}
This map defines a new model of the local $L_\infty$ algebra, which we will call $\cL_\infty$. The notation refers to the fact that this new model has nonvanishing $L_\infty$ brackets of every order. It is this new model that we will use to define the eleven-dimensional theory of twisted supergravity (as well as the family of analogous formal moduli problems on products of odd Calabi--Yau manifolds with~$\R$). 
\ingmar{I want to write the other automorphism later, I think; otherwise we have to write the composition, since we presented it on bcov}

%The previous proposition characterizes the $L_\infty$ model for divergence-free vector fields that we will use to define the 11-dimensional theory of twisted supergravity. 
%Hereon, we denote by $\cL_0 = \cE_0[-1]$ this local $L_\infty$ algebra.

%We can unpack Proposition \ref{prop:Linfty} to describe the $L_\infty$ structure on $\cL_0$ explicitly. 
We can describe the $L_\infty$ structure on our new model $\cL_\infty$ more explicitly.
Recall that we have two types of elements: $\mu \in \PV^{1,\bu}$ and $\nu \in \PV^{0,\bu}[-1]$. 
The first few nonzero brackets are
\begin{align*}
[\mu]_1 & = \dbar \mu + \div \mu \\
[\mu_1,\mu_2]_2 & = \div (\mu_1 \mu_2) \\
[\nu, \mu_1,\mu_2]_3 & = \div(\nu \mu_1 \mu_2) \\
[\nu_1,\nu_2, \mu_1,\mu_2]_4 & = \# \div(\nu_1 \nu_2 \mu_1 \mu_2).
\end{align*}
For $k \geq 2$ the general formula for the $k$-ary bracket is 
\[
[\nu_1,\nu_2, \ldots, \nu_{k-2}, \mu_1,\mu_2]_{k} = \# \div(\nu_1 \cdots \nu_k \mu_1 \mu_2) .
\]

@@

Recall further that we constructed two equivalent descriptions of the BF theory based on divergence-free holomorphic vector fields above. Since we are now in the context of a nondegenerate BV theory, the differential is Hamiltonian, and can be incorporated into the action functional by including a quadratic term; we do this from now on. The first action functional is obtained by considering the BF theory associated to the natural dg Lie structure on the complex modeling divergence-free vector fields (inherited from the Schouten bracket). This takes the form
\deq{
  I_\strict = \beta\partial_\Omega \mu + \frac{1}{2} \gamma [\mu,\mu] + \beta[\mu,\nu].
}
The other action is of infinite order. (In fact, it is related to the BCOV action functional via a procedure we outline below.)\ingmar{or somewhere} Explicitly, this action functional is given by 
\deq{
  I_\infty = \beta \partial_\Omega \mu + \frac{1}{1-\nu} (\partial \gamma) \mu^2.
}

We demonstrated above that the two local $L_\infty$ algebras on which these BF theories are based are equivalent. As such, the BF theories are also equivalent; the map~\eqref{eq:newbase} extends uniquely to a Poisson automorphism of the Lie algebra cochains of the BF theory, which defines an equivalence of cyclic $L_\infty$ algebras. \ingmar{how should we say this} Explicitly, the map is given by
\deq{
  \nu \mapsto 1-e^{-\nu}, \ldots
}
\subsection{A family of deformations}

@@

\subsection{Further equivalences}
